Gaussian mean estimation in simulated data sets

### 2019-12-31 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

```{r summarize-results-homo, fig.height=4, fig.width=8}
create.bar.plots(rbind(
  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
```

@@

>>>>

```{r summarize-results-homo, fig.height=4, fig.width=8}
create.bar.plots.homosked(rbind(
  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
```

@@

Combined results from simulated data sets with heteroskedastic errors
---------------------------------------------------------------------

These plots summarize the results from all combinations of test
functions and a signal-to-noise ratio of 1.

```{r summarize-results-heterosked-snr-1, fig.height=4.5, fig.width=9}
create.bar.plots.heterosked(rbind(
  data.frame(mean="sp",  var="v2",snr=1,get.results.heterosked(res,"sp.1.v2")),
  data.frame(mean="sp",  var="v3",snr=1,get.results.heterosked(res,"sp.1.v3")),
  data.frame(mean="sp",  var="v4",snr=1,get.results.heterosked(res,"sp.1.v4")),
  data.frame(mean="sp",  var="v5",snr=1,get.results.heterosked(res,"sp.1.v5")),
  data.frame(mean="bump",var="v2",snr=1,get.results.heterosked(res,"bump.1.v2")),
  data.frame(mean="bump",var="v3",snr=1,get.results.heterosked(res,"bump.1.v3")),
  data.frame(mean="bump",var="v4",snr=1,get.results.heterosked(res,"bump.1.v4")),
  data.frame(mean="bump",var="v5",snr=1,get.results.heterosked(res,"bump.1.v5")),
  data.frame(mean="blk", var="v2",snr=1,get.results.heterosked(res,"blk.1.v2")),
  data.frame(mean="blk", var="v3",snr=1,get.results.heterosked(res,"blk.1.v3")),
  data.frame(mean="blk", var="v4",snr=1,get.results.heterosked(res,"blk.1.v4")),
  data.frame(mean="blk", var="v5",snr=1,get.results.heterosked(res,"blk.1.v5")),
  data.frame(mean="ang", var="v2",snr=1,get.results.heterosked(res,"ang.1.v2")),
  data.frame(mean="ang", var="v3",snr=1,get.results.heterosked(res,"ang.1.v3")),
  data.frame(mean="ang", var="v4",snr=1,get.results.heterosked(res,"ang.1.v4")),
  data.frame(mean="ang", var="v5",snr=1,get.results.heterosked(res,"ang.1.v5")),
  data.frame(mean="dop", var="v2",snr=1,get.results.heterosked(res,"dop.1.v2")),
  data.frame(mean="dop", var="v3",snr=1,get.results.heterosked(res,"dop.1.v3")),
  data.frame(mean="dop", var="v4",snr=1,get.results.heterosked(res,"dop.1.v4")),
  data.frame(mean="dop", var="v5",snr=1,get.results.heterosked(res,"dop.1.v5")),
  data.frame(mean="blip",var="v2",snr=1,get.results.heterosked(res,"blip.1.v2")),
  data.frame(mean="blip",var="v3",snr=1,get.results.heterosked(res,"blip.1.v3")),
  data.frame(mean="blip",var="v4",snr=1,get.results.heterosked(res,"blip.1.v4")),
  data.frame(mean="blip",var="v5",snr=1,get.results.heterosked(res,"blip.1.v5")),
  data.frame(mean="cor", var="v2",snr=1,get.results.heterosked(res,"cor.1.v2")),
  data.frame(mean="cor", var="v3",snr=1,get.results.heterosked(res,"cor.1.v3")),
  data.frame(mean="cor", var="v4",snr=1,get.results.heterosked(res,"cor.1.v4")),
  data.frame(mean="cor", var="v5",snr=1,get.results.heterosked(res,"cor.1.v5"))))
```

These plots summarize the results from data sets simulated using a
signal-to-noise ratio of 3.

```{r summarize-results-heterosked-snr-3, fig.height=4.5, fig.width=9}
create.bar.plots.heterosked(rbind(
  data.frame(mean="sp",  var="v2",snr=1,get.results.heterosked(res,"sp.3.v2")),
  data.frame(mean="sp",  var="v3",snr=1,get.results.heterosked(res,"sp.3.v3")),
  data.frame(mean="sp",  var="v4",snr=1,get.results.heterosked(res,"sp.3.v4")),
  data.frame(mean="sp",  var="v5",snr=1,get.results.heterosked(res,"sp.3.v5")),
  data.frame(mean="bump",var="v2",snr=1,get.results.heterosked(res,"bump.3.v2")),
  data.frame(mean="bump",var="v3",snr=1,get.results.heterosked(res,"bump.3.v3")),
  data.frame(mean="bump",var="v4",snr=1,get.results.heterosked(res,"bump.3.v4")),
  data.frame(mean="bump",var="v5",snr=1,get.results.heterosked(res,"bump.3.v5")),
  data.frame(mean="blk", var="v2",snr=1,get.results.heterosked(res,"blk.3.v2")),
  data.frame(mean="blk", var="v3",snr=1,get.results.heterosked(res,"blk.3.v3")),
  data.frame(mean="blk", var="v4",snr=1,get.results.heterosked(res,"blk.3.v4")),
  data.frame(mean="blk", var="v5",snr=1,get.results.heterosked(res,"blk.3.v5")),
  data.frame(mean="ang", var="v2",snr=1,get.results.heterosked(res,"ang.3.v2")),
  data.frame(mean="ang", var="v3",snr=1,get.results.heterosked(res,"ang.3.v3")),
  data.frame(mean="ang", var="v4",snr=1,get.results.heterosked(res,"ang.3.v4")),
  data.frame(mean="ang", var="v5",snr=1,get.results.heterosked(res,"ang.3.v5")),
  data.frame(mean="dop", var="v2",snr=1,get.results.heterosked(res,"dop.3.v2")),
  data.frame(mean="dop", var="v3",snr=1,get.results.heterosked(res,"dop.3.v3")),
  data.frame(mean="dop", var="v4",snr=1,get.results.heterosked(res,"dop.3.v4")),
  data.frame(mean="dop", var="v5",snr=1,get.results.heterosked(res,"dop.3.v5")),
  data.frame(mean="blip",var="v2",snr=1,get.results.heterosked(res,"blip.3.v2")),
  data.frame(mean="blip",var="v3",snr=1,get.results.heterosked(res,"blip.3.v3")),
  data.frame(mean="blip",var="v4",snr=1,get.results.heterosked(res,"blip.3.v4")),
  data.frame(mean="blip",var="v5",snr=1,get.results.heterosked(res,"blip.3.v5")),
  data.frame(mean="cor", var="v2",snr=1,get.results.heterosked(res,"cor.3.v2")),
  data.frame(mean="cor", var="v3",snr=1,get.results.heterosked(res,"cor.3.v3")),
  data.frame(mean="cor", var="v4",snr=1,get.results.heterosked(res,"cor.3.v4")),
  data.frame(mean="cor", var="v5",snr=1,get.results.heterosked(res,"cor.3.v5"))))
```
